Turbulence in compact to giant H~II regions

### 2023-04-27 strucfunc_paper.tex
Finish last part of NGC 595. Just 604 to go.

\subsubsection{Observed structure function and model fit}
\label{sec:observ-struct-funct-m33}

In Figure~\ref{fig:strucfunc-fit-ExtraGal}c we show the structure function of NGC 595.
The model-derived parameters are \(\sigma\pos^2 = \SI{53 \pm 5}{km^{2}.s^{-2}}\),
\(r_0 = \SI{11 \pm 1.0}{pc} \)), and \(m = 1.4 \pm 0.2\).
The velocity variance is slightly higher than the observed value of \SI{44}{km^{2}.s^{-2}},
indicative of a moderate finite box effect.
At the largest scales, the structure function trends slowly downwards,
which may be due to a radial decline in the amplitude of the turbulent velocity field,
but the effect is less marked than in other regions, such as Orion.

In  Figure~\ref{fig:strucfunc-fit-ExtraGal}d we show the structure function of NGC 604.
The model-derived parameters are \(\sigma\pos^2 = \SI{84 \pm 20}{km^{2}.s^{-2}}\),
\(r_0 = \SI{12 \pm 6}{pc} \)), and \(m = 0.8 \pm 0.2\).
Again the model-derived velocity variance is higher than the observed value of \SI{55}{km^{2}.s^{-2}},
which this time is due primarily to the fact that the
derived correlation length is only 6 times higher than the RMS seeing width,
so some of the small-scale fluctuation power is missing from the observations.
Of all our sources, NGC~604 shows the largest difference between the inferred
``true'' structure function and the observed one, so the derived parameters
should be treated with caution.
At the largest scales, the structure function shows a pronounced minimum
at \(r \approx {150}{pc}\), which may be due to a periodic oscillation with \(\lambda \approx {300}{pc}\),
which is slightly larger than the size of the map.

@@

\citet{lagrois2011} calculated the structure function for the \halpha\ emission line for NGC 595
over a region of diameter \SI{300}{kpc} with a resolution of \SI{6.6}{pc.pixel^{-1}} \citep{lagrois2009multi}, presenting results for separations \(r \ge \SI{16.5}{pc}\).
They found a total velocity variance of \(\sigma\pos^2 = \SI{35 \pm 2}{km^{2}.s^{-2}}\), which is smaller than our derived value of \(\sigma\pos^2 = \SI{53}{km^{2}.s^{-2}}\).

For our NGC 595 \halpha\ emission line results there is no correspondence in the structure function from the previous investigations of \citet{lagrois2009multi} and \citet{lagrois2011}.
Our observations cover the brightest part of the region and have smaller resolution than theirs.
As a consequence \citet{lagrois2009multi} and \citet{lagrois2011} structure functions results does not cover scales $<$10 pc, where in our results the correlation is taking place.
One big difference is that \citet{lagrois2011} apply a  filter to the velocity field to get rid of non-turbulent movements.
As a comparison, for the filtered turbulent parameters they chose to represent the turbulent field, the derive a total  decorrelation length (\(C(\tau_0) = 0\)) of \SI{43}{pc} and the power-law index they provide is \num{1.55 \pm 0.01}.
Their velocity centroid \(\sigma\) is \SI{5.92 \pm 0.15}{km.s^{-1}} while we have \SI{7.3\pm 2}{km. s^{-1}} which fall within the uncertainties.
Due to the different observations and methodologies a direct comparison between structure functions is not possible.

>>>>

\startNEW
\subsubsection{Observed structure function and model fit}
\label{sec:observ-struct-funct-m33}
\stopNEW

In Figure~\ref{fig:strucfunc-fit-ExtraGal}c we show the structure function of NGC 595.
\startNEW
The model-derived parameters are \(\sigma\pos^2 = \SI{53 \pm 5}{km^{2}.s^{-2}}\),
\(r_0 = \SI{11 \pm 1.0}{pc} \)), and \(m = 1.36 \pm 0.15\).
The velocity variance is slightly higher than the observed value of \SI{44}{km^{2}.s^{-2}},
indicative of a moderate finite box effect.
At the largest scales, the structure function trends slowly downwards,
which may be due to a radial decline in the amplitude of the turbulent velocity field,
but the effect is less marked than in other regions, such as Orion. 
\stopNEW

In  Figure~\ref{fig:strucfunc-fit-ExtraGal}d we show the structure function of NGC 604.
\startNEW
The model-derived parameters are \(\sigma\pos^2 = \SI{84 \pm 20}{km^{2}.s^{-2}}\),
\(r_0 = \SI{12 \pm 6}{pc} \)), and \(m = 0.8 \pm 0.2\).
Again the model-derived velocity variance is higher than the observed value of \SI{55}{km^{2}.s^{-2}},
which this time is due primarily to the fact that the
derived correlation length is only 6 times higher than the RMS seeing width,
so some of the small-scale fluctuation power is missing from the observations.
Of all our sources, NGC~604 shows the largest difference between the inferred
``true'' structure function and the observed one, so the derived parameters
should be treated with caution.
At the largest scales, the structure function shows a pronounced minimum
at \(r \approx {150}{pc}\), which may be due to a periodic oscillation with \(\lambda \approx {300}{pc}\),
which is slightly larger than the size of the map. 
\stopNEW

@@

\citet{lagrois2011} calculated the structure function for the \halpha\ emission line for NGC 595
over a region of diameter \SI{300}{kpc} with a resolution of \SI{6.6}{pc.pixel^{-1}} \citep{lagrois2009multi}, presenting results for separations \(r \ge \SI{16.5}{pc}\).
They found a total velocity variance of \(\sigma\pos^2 = \SI{35 \pm 2}{km^{2}.s^{-2}}\), which is smaller than our derived value of \(\sigma\pos^2 = \SI{53}{km^{2}.s^{-2}}\).
Our map covers a smaller region, so part of the reason for this discrepancy may be
a radial decline in the velocity variance, as mentioned above.
Another reason may be that the angular resolution of the \citet{lagrois2009multi} map
is of the same order as the correlation length, so some of the small-scale power is missing.

\citet{lagrois2011} employ a novel technique based on filtering the
bidimensional velocity field to remove large-scale non-turbulent motions
before calculating the structure function.
They find a total decorrelation length of \(\tau_0 = \SI{43}{pc}\) and a very steep
power-law index of \(m = \num{1.55 \pm 0.1}\).
As discussed in section~\ref{sec:comp-with-prev}, \(\tau_0\) is predicted to be 2--3 times larger than \(r_0\), given the way that we define the correlation length,
but even taking this into account, our derived value is still smaller than theirs
by at least 50\%.
Although this may be due to the difference in the areas covered,
it is more likely due to the lower resolution of the \citeauthor{lagrois2011} data.

The power-law index is somewhat steeper than our own value,
but in part this is due to differences in methodology:
the width of the low-pass filter that \citeauthor{lagrois2011} use to remove large-scale
motions is \SI{8}{pixels} or \SI{53}{pc}, which is comparable to the decorrelation length.
As a result, subtracting the filtered data causes a clear steepening of the structure function,
as can be seen in their Figure~6d.
The unfiltered data can be seen to show a shallower slope, more consistent
with our own results.
Which result is more reliable is difficult to say, but could potentially be checked
by experimenting on fake data in a similar fashion to our Appendix~\ref{sec:degr-struct-funct}.
